---
title: "cranium"
author: Ben Baumer
date: April 11, 2017
output:
  md_document:
    variant: markdown_github
---

An R package to quantify radial bridge images

## Installation

`cranium` depends on the `rhdf5` package for reading HDF5 files, but this package is not available on CRAN. You must install it from Bioconductor. To do this, you have to run the following code once:

```{r, eval=FALSE}
install.packages("BiocInstaller",
                 repos = "http://bioconductor.org/packages/3.4/bioc")
source("https://bioconductor.org/biocLite.R")
biocLite("rhdf5")
```

Then, you can install `cranium` from GitHub using the following commands:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("beanumber/cranium")
library(cranium)
```

## Download sample data
To download sample data, You Too and WildType, you can run:

```{r}
youtoo <- download_youtoo_data("folder") #where folder is the location you want to store the You Too data
wildtype <- download_wildtype_data("folder") #where folder is the location you want to store the Wild Type data
youtoo[[1]] #first you too data sample
```
Once the above is ran, the files are saved in a list and in the folder you set, each data sample can be indivudually picked from list by indexing.

## Plot a 3D image of a brain

Now, you can simply point to a raw HDF5 file, and quickly render a 3D image of the data, along with our model of it. 

```{r, eval=FALSE}
file <- "~/Data/barresi/AT_1_Probabilities.h5"
library(cranium)
library(tidyverse)
tidy_brain <- file %>%
  read_h5() %>%
  tidy()
plot3d(tidy_brain)
```
